\section{Course integration}\label{sec:course-integration}
% How does our project use knowledge which we've learned through our courses in the first and second year?
This project is a sequel of its predecessors P\&O 1 and P\&O 2. So most knowledge and experience that's been used for this project came from these courses. In these courses items like writing reports (in \LaTeX), keeping track of a logbook, making presentations, ect. were taught. These are basic aspects needed for creating a good project. As mentioned earlier, the experience that has been gained from these courses is also very important. From these courses the skill of working in a team were developed, which was very important for this project and will remain important for future projects. \\

\noindent Furthermore, methodology of computer science was an important course for an introduction to programming and understanding complex algorithms. This course was taught in Python and this knowledge was needed for the Raspberry Pi and licence plate recognition. Along with Python, Dart was used and this language was easy to learn because of this course.  \\

\noindent Just like methodology of computer science was used for the licence plate recognition, other courses like calculus and linear algebra were needed for neural networks. Calculus was useful for solving the optimisation problems in the neural network, to find the best solution. Linear algebra is used in the neural networks for solving large systems of linear equations. \\  

\noindent Another course that was very useful, was technical drawing for creating our physical design in Solid Edge. In this course the skills were taught for creating a 3D-design of an object or product and understanding the 2D-drawings of it. Other knowledge that was used for the physical aspect of the project was circuit design. This was taught in P\&O 2 and was used for the sensors and lights. For creating these electronic circuits, knowledge from the course electrical networks was also necessary. This course was needed for understanding how to connect different electronic components with each other.\\

\noindent Of course was the knowledge of all these courses not enough to make and realise this project. But it's a good basis to understand and learn new advanced topics in this field.  

\clearpage
\addcontentsline{toc}{section}{References}
\bibliographystyle{apalike}
\bibliography{bibliography}

\clearpage